---
title: | 
       | Centered: 
       | Title
author: 'Your Name'
csl: ASA_format.csl
output:
  pdf_document:
    includes:
      in_header: preamble.tex
    number_sections: true
    keep_tex: yes
    latex_engine: xelatex
geometry:
- top=1in
- bottom=1in
- right=1in
- left=1in
mainfont: Georgia
documentclass: DissertateCUNY
params:
  abstract: 'Write your abstract here but keep in between quotes. ' 
  advisor: Advisor Name
  chair: Chair Name
  committee1: Prof 1, Advisor
  committee2: Prof 2, First Reader
  committee3: Prof 3
  committee4: Prof 3
  degree: Doctor of Philosophy
  executiveOfficer: Executive Officer
  field: Sociology
  approved: December
  yearapproved: '2022' # could be different if applying for Feb graduation
  year: '2022'
bibliography: references.bib
---

```{r global_options, include=FALSE}
## This saves you from having to do this for every chunk
knitr::opts_chunk$set(fig.path = 'figures/', # In code chunks, I use here() package to reference to figures and tables, but this is another option
                      echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)

## Do NOT Remove / adds params to doc
cat(paste0("\\usepackage{xspace}\n",
           "\\newcommand{\\yeardegree}{",params$year,"\\xspace}",
            "\\newcommand{\\yearapproved}{",params$yearapproved,"\\xspace}\n",
           "\\newcommand{\\degree}{",params$degree,"\\xspace}\n",
           "\\newcommand{\\field}{",params$field,"\\xspace}\n",
           "\\newcommand{\\approved}{",params$approved,"\\xspace}\n",
           "\\newcommand{\\chairperson}{", params$chair, "\\xspace}\n",
           "\\newcommand{\\committeeone}{", params$committee1, "\\xspace}\n",
           "\\newcommand{\\committeetwo}{", params$committee2, "\\xspace}\n",
           "\\newcommand{\\committeethree}{", params$committee3, "\\xspace}\n",
           "\\newcommand{\\committeefour}{", params$committee4, "\\xspace}\n",
           "\\newcommand{\\gradschoolguy}{", params$gradschool, "\\xspace}\n",
           "\\newcommand{\\EO}{", params$executiveOfficer, "\\xspace}\n",
           "\\newcommand{\\advisor}{", params$advisor, "\\xspace}\n",
           "\\newcommand{\\abstract}{", params$abstract, "\\xspace}\n",
           "% Tables
           \\usepackage{booktabs}
           \\usepackage{threeparttable}
           \\usepackage{array}
           \\newcolumntype{x}[1]{%
           >{\\centering\\arraybackslash}m{#1}}%
           \\usepackage{placeins}
           \\usepackage{chngcntr}
           \\counterwithin{figure}{chapter}
           \\counterwithin{table}{chapter}
           \\usepackage{lipsum}
           \\usepackage[makeroom]{cancel}\n"
           ),file = "preamble.tex")
```

<!-- Title page printed automatically -->
\copyrightpage
\approvalpage
\abstractpage


<!-- Acknowledgements -->
\newpage
\fancyhead[L]{Acknowledgments}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\chapter*{ACKNOWLEDGEMENTS}
\addcontentsline{toc}{section}{Acknowledgments}

Acknowledge them.

 
<!-- Front Matter -->
\newpage
\fancyhead[L]{Table of Contents}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\tableofcontents

\newpage
\fancyhead[L]{List of Tables}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\listoftables

\newpage
\fancyhead[L]{List of Figures}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\listoffigures


<!-- Dedication -->
\newpage
\fancyhead[L]{Dedication}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\chapter*{DEDICATION}
\addcontentsline{toc}{section}{Dedication}


\hspace{0pt}
\vfill
\textit{Dedicate it here.}
\vfill
\hspace{0pt}



\newpage
\pagenumbering{arabic}

<!-- Chapter 1 -->
\newpage
\fancyhead[L]{Chapter 1: Running head}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter{Chapter 1: Introduction}

```{r child = 'chapters/chp1.Rmd'}
```

\FloatBarrier

<!-- Chapter 2 -->
\newpage
\fancyhead[L]{Chapter 2: Running head}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter{Chapter 2: Full title}

```{r child = 'chapters/chp2.Rmd'}
```

\FloatBarrier

<!-- Chapter 3 -->
\newpage
\fancyhead[L]{Chapter 3: Running head}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter{Chapter 3: Full title}

```{r child = 'chapters/chp3.Rmd'}
```

\FloatBarrier

<!-- Appendices -->
\newpage

\fancyhead[L]{Appendices}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\chapter*{APPENDICES}
\addcontentsline{toc}{chapter}{APPENDICES}

<!-- appendix -->
```{r child = 'chapters/appendix.Rmd'}
```

\FloatBarrier

<!-- References -->
\newpage

\fancyhead[L]{References}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter*{REFERENCES}
\singlespacing
\addcontentsline{toc}{chapter}{REFERENCES}

<!-- \setlength{\parindent}{-0.5in} -->
<!-- \setlength{\leftskip}{0.5in} -->
\setlength{\parskip}{6pt}
\noindent

<div id="refs"></div>
\clearpage


